### 2021-04-22 docs/manuscript/PLOS-MSc-Thesis.tex
Fix typo: wich -> which

The neutral network (a metagraph in wich each node is a network topology)
shows that most of the network topologies are grouped into a connected graph.
This graph is composed of 639 nodes that are accessible by one mutational step.
The 15 most abundant network topologies, with the exception of
number 10, are part of this graph (Fig~\ref{fig:neutral-network}). We also
found nodes inside the neutral network that had more connections between them
than with other nodes, generating clusters of nodes, interestingly in
almost every cluster is present one or more of the 15 most abundant network
topologies. In addition, we found that the first eight most abundant network
topologies were located in the largest cluster.

>>>>

The neutral network (a metagraph in which each node is a network topology)
shows that most of the network topologies are grouped into a connected graph.
This graph is composed of 639 nodes that are accessible by one mutational step.
The 15 most abundant network topologies, with the exception of
number 10, are part of this graph (Fig~\ref{fig:neutral-network}). We also
found nodes inside the neutral network that had more connections between them
than with other nodes, generating clusters of nodes, interestingly in
almost every cluster is present one or more of the 15 most abundant network
topologies. In addition, we found that the first eight most abundant network
topologies were located in the largest cluster.
